My Statistics 3494W Proposal

### 2022-10-05 Proposal/Proposal.tex
commit #ResearchDesign

>>>>

\section*{Research Design}
I will be using Rstudio to create a model to forecast the call center data. I plan on doing research on previous ways call center data
has been forecast before. I am planning on creating multiple models based on a 15 minute interval using liner regression, poisson distribution,
and autoregressive integrated moving average (ARIMA) models \citep*{ibrahim2016modeling}. By creating figures I can
easily describe the patterns to my audience. These methods can clearly show a pattern which I can use to back up my claims on how many 
employees should be present at certain times. Once I can find a clear distribution to describe the call center patterns, I will be
able to possibly going into further detail describing if there is a relationship between call length and call reason, and if all agents are
performing at the same level. With these methods, I believe I can investigate and answer the research question.
